Open-source landscape for 3D CSEM modelling

### 2020-07-07 manuscript/Manuscript.tex
Fix all errors reported in Overleaf

Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing OcTree meshes. Furthermore, as a part of a broader development objective of interoperating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0 \citep{simpeg0.14.0}. }

>>>>

Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing OcTree meshes. Furthermore, as a part of a broader development objective of interoperating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
% \citep{simpeg0.14.0}.
}
